---
title: "Linear Models"
author: "Linh Tran"
date: "11/21/2020"
output: 
    html_document:
      toc: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d


set.seed(1)

```

# Linear models

Load data

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(borough != "Staten Island") %>% 
  select(price, stars, borough, neighborhood, room_type)

```

## Model fitting

Scatterplot:

```{r}
#price = continuous variable, stars = numeric predictor, borough = categorical predictor

nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price, color = borough)) +
  geom_point()
```

Fit a model consider price as an outcome that may depend on rating and borough

```{r}
fit = lm(price ~ stars + borough, data = nyc_airbnb)
fit
```


## Tidying output

Look at the result

```{r, include = FALSE}
fit
summary(fit)
summary(fit)$coef
coef(fit)
fitted.values(fit)
residuals(fit)

broom::glance(fit)  #gives me some useful numbers
```

Better way to look at the result:

```{r}

broom::tidy(fit) %>% #structured as a df
  select(-std.error, -statistic) %>% 
  mutate(
    term = str_replace(term, "borough", "Borough: ")
  ) %>% 
  knitr::kable(digits = 3)
```

## Be in control of factors

R treat categorical (factor) covariates as such: indicator variables are created for each non-reference category and included in model, and the factor level is treated as the reference.

```{r}
nyc_airbnb =
  nyc_airbnb %>% 
  mutate(
    borough = fct_infreq(borough),
    room_type = fct_infreq(room_type)
  )

nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price, color = borough)) +
  geom_point()
```

Refit my model: now Manhattan is the reference 

```{r}
fit = lm(price ~ stars + borough, data = nyc_airbnb)

broom::tidy(fit)
```


## Diagnostics

```{r}
modelr::add_residuals(data = nyc_airbnb, model = fit)
# First one is $9.47 higher than what my model predicts.
```

Look at distribution of residuals:

```{r}
modelr::add_residuals(data = nyc_airbnb, model = fit) %>% 
  ggplot(aes(x = borough, y = resid)) +
  geom_violin() +
  ylim(-500, 1500)

#Distributions of residuals are skewed. 

nyc_airbnb %>% 
  modelr::add_residuals(fit) %>% 
  ggplot(aes(x = stars, y = resid)) +
  geom_point() +
  facet_wrap(. ~ borough)

#Distributions of residual spread out as star counts increases. 
```

## Hypothesis testing

This does t-test by default

```{r}
fit %>% 
  broom::tidy()
```

Significance of `borough`

```{r}
fit_null = lm(price ~ stars, data = nyc_airbnb)
fit_alt = lm(price~stars + borough, data = nyc_airbnb)

anova(fit_null, fit_alt) %>% 
  broom::tidy()
```


## Nesting data



## Binary outcomes


# Cross Validation





# Bootstrapping
